\section{Lecture 9 - Scaling of OSN} % (fold)
\label{sec:lecture_9_scaling_of_osn}

\subsection{Introduction to OSN Scaling}
As Online Social Networks are extremely popular,
their demand for a scalable infrastructure to support their growth is natural.
Cloud COmputing can provide such scaling,
but it leads to some problems that need to be dealt with.

Conventional scaling approaches are horizontal or vertical.
Where \emph{vertical} stands for the the upgrading the existing hardware.
This can be expensive and be technically infeasible.
\emph{Horizontal} scaling means deploying a larger number of servers
and distributing the workload amongst them.
Although this is only suitable for stateless front-end servers,
on back-end storage servers the data must be partitioned into disjoint components.

Bot approaches are not applicable to OSNs,
as the large amount of data rules out vertical scaling 
and the large amount of interconnect makes horizontal scaling infeasible.
This refers to the fact that in an OSN,
most operations are between users and their neighbors.
Their data is usually placed on multiple servers
and the mu 'multi-get' operations generate a huge amount of traffic
and unpredictable response times.

\subsection{Social Paritioning and Replication} % (fold)
\label{sub:social_paritioning_and_replication}
A novel solution for these problems could be \emph{SPAR} (Social Partitioning And Replication).
Its approach is to have a one-hop replication
so that all neighbors of users are replicated on the same server.
This leads to a 'Social Locality'.\\
The requirements for SPAR are:
	\begin{itemize}
		\item Maintain local semantics
		\item Balance loads
		\item Be resilient to machine failures
		\item Be amenable to online operations
		\item Be stable
		\item Minimize the replication overhead
	\end{itemize}
% subsection social_paritioning_and_replication (end)

\subsection{OSN in the Cloud} % (fold)
\label{sub:osn_in_the_cloud}
OSNs require features that can be delivered very well with cloud computing.
The networks need to be available in a reliable fashion
on a global scale.
They also require high amounts of flexibility in the amount of workload they can do.

Cloud computing can provide the availability, flexibility and scalability required by OSNs.
Due to the 'pay-as-you-go' plans the cost do not have to paid in front.
The cloud allows to serve customers,
but keep the cost at a low level.
Although the Quality of Service (QoS) must be maintained.

\subsubsection{Cloud QoS} % (fold)
\label{ssub:cloud_qos}
There is always a trade off between the quality of the service and the cost.
In OSNs this is especially difficult,
as new users join and old users leave.
The overall goal is to maximize QoS and minimize the cost.

In a multi-cloud scenario,
one can rank the clouds for each user according to metrics like access time.
One can then use a vector approach and try to find out on which nodes or clouds of the networks
certain user data shall be stored to keep access times low as well as costs.

\paragraph{Cosplay} % (fold)
\label{par:cosplay}
is an algorithm that can be applied to this problem.
It allows to swap the roles between master and slave replicas,
which can be feasible in to reduce the costs.
it is important here to maintain social locality of the users data.
% paragraph cosplay (end)
% subsubsection cloud_qos (end)

\subsubsection{Social data placement in Data-centers} % (fold)
\label{ssub:social_data_placement_in_datacenters}
In Data centers it is important how the data is spread across the nodes.
Here the goals are to minimize the traffic that is routed through the highest tiers of the network,
the core.
The second goal is to minimize the traffic that has to traverse any switch.\\
It might be feasible to switch the roles of master and slave replicas.
This can lead to a reduction of traffic,
as social locality is maintained which leads to less data having to leave the node.
% subsubsection social_data_placement_in_datacenters (end)
% subsection osn_in_the_cloud (end)
% section lecture_9_scaling_of_osn (end)