\section{Lecture 4 - Social Networks: Structure \& Properties} % (fold)
\label{sec:social_networks_structure_&_properties}

Networks can characterized in different ways.
Distinctive features are:\\
\begin{description}
	\item[Degree Distribution] How many Neighbors has a node?
	\item[Average Path Length] Whats the mean number of hops between nodes?
	\item[Network Diameter] How far apart are the nodes?
	\item[Distance - Shortest Path] How big is the network?
	\item[Clustering Coefficient] How close is a set of nodes connected with each other?
	\item[Community] Are subsets more closely connected?
\end{description}

\subsection{Network Properties} % (fold)
\label{sub:network_properties}
	The key Network properties are described in this Section,
	Degree Distribution, Path Length and Clustering Coefficient.

	\subsubsection{Degree Distribution} % (fold)
	\label{ssub:degree_distribution}
	The degree distribution $P(k)$ describes the probability of randomly given node,
	having the degree $k$.
	It can be calculated as described in Equation \ref{eq:degree_distribution}.

	\begin{equation}
	\label{eq:degree_distribution}
		P(k) = N_k / N
	\end{equation}

	Where $N_k$ is the number of nodes.
	% subsubsection degree_distribution (end)

	\subsubsection{Path Length} % (fold)
	\label{ssub:path_length}
		The Path Length subsumes several metrics for the network size.
		\paragraph{Distance} % (fold)
		\label{par:distance}
		describes the number of edges across the shortest path on the network.
		This also means that if two nods are not connected,
		their distance is infinite.
		% paragraph distance (end)

		\paragraph{Diameter} % (fold)
		\label{par:diameter}
		is the maximum distance in terms of edges between any nodes of the network.
		It is the opposite metric to the distance.
		% paragraph diameter (end)

		\paragraph{Average Path Length} % (fold)
		\label{par:average_path_length}
		is the combined measurement of the distance and the diameter,
		taking the average distance between all the nodes in the network.
		% paragraph average_path_length (end)
	% subsubsection path_length (end)

	\subsubsection{Clustering Coefficient} % (fold)
	\label{ssub:clustering_coefficient}
		This metric evaluated how the neighbors of a node are interconnected.
		For a given node $i$ with the degree $k$,
		assume the number of neighbors of $i$ is $e$,
		then the clustering coefficient of $i$ is described in equation \ref{eq:clustercoefficient}.
		\begin{equation}
		\label{eq:clustercoefficient}
		C_i - \frac{e}{k(k - 1)/2}
		\end{equation}

		The average Clustering Coefficient for network is then:
		\begin{equation}
		\label{eq:averagecc}
		C = \frac{1}{N} \sideset{}{_i^N}\sum C_i
		\end{equation}
	% subsubsection clustering_coefficient (end)

	\subsubsection{Degree Centrality} % (fold)
	\label{ssub:degree_centrality}
		This measurement determines how connected is a certain node inside the network.
		\begin{equation}
		\label{eq:degreecentrality}
			d_i(g) / (n-g)
		\end{equation}
	% subsubsection degree_centrality (end)

	\subsubsection{Closeness Centrality} % (fold)
	\label{ssub:closeness_centrality}
		Given the Closeness Centrality one can determine,
		how easily a node can reach other nodes in the network.
		\begin{equation}
		\label{eq:closenesscentrality}
			(n-1) / \sum_{j\neq i} l(i,j)
		\end{equation}
		Where $l(i,j)$ is the length of the shortest path between the nodes i and j.
	% subsubsection closeness_centrality (end)

	\subsubsection{Betweenness Centrality} % (fold)
	\label{ssub:betweenness_centrality}
		The Betweenness Centrality of a node gives a measurement how important a node is,
		in terms of connecting other nodes of the network.
		\begin{equation}
		\label{eq:betweennesscentrality}
			Ce_i^B (g) = \sum_{k\neq j:i\notin\{k,j\}} \frac{P_i(kj)/P(kj)}{(n-1)(n-2)/2}
		\end{equation}	
	% subsubsection betweenness_centrality (end)
% subsection network_properties (end)

\subsection{Metrics of typical networks} % (fold)
\label{sub:metrics_of_typical_networks}

	\subsubsection{Complete Graph} % (fold)
	\label{ssub:complete_graph}
	All nodes are interconnected.
		\begin{description}
			\item[Degree Distribution] $P(k) = N-1$
			\item[Path Length] Diameter = 1 --- Average Path Length = 1
			\item[Clustering Coefficient] C = 1 --- Average Clustering Coefficient = 1
		\end{description}
	% subsubsection complete_graph (end)

	\subsubsection*{Regular Latice} % (fold)
	\label{ssub:regular_latice}
	A Ring connecting only neighbors.
	Each node is also connected to its successors and its predecessors neighbor.
	\begin{description}
			\item[Degree Distribution] $P(k) = N-1$
			\item[Path Length] Diameter = 1 --- Average Path Length = 1
			\item[Clustering Coefficient] C = 1 --- Average Clustering Coefficient = 1
		\end{description}
	% subsubsection regular_latice (end)

	\subsubsection{Random Graph} % (fold)
	\label{ssub:random_graph}
	This depends on how the random graph is generated.
	Here we assume a binomial distribution.
		\begin{description}
			\item[Degree Distribution] $P(k) = \binom{n-1}{k}p^k(1-p)^{n-1-k}$
			\item[Average Path Length] $O(\log n)$
			\item[Clustering Coefficient] $C = p = \bar{k}/n$
		\end{description}
	% subsubsection random_graph (end)
% subsection metrics_of_typical_networks (end)

\subsection{Power Law} % (fold)
\label{sub:power_law}
When observing the popularity of nodes in a network,
one can see that there is an imbalance.
Some nodes have far higher degrees and receive more connections than others.
A typical example is that 20\% of the websites,
receive 80\% of the traffic.
This effect can be observed in many other networks like twitter,
where celebrities have a huge amount of followers,
or the imbalance of money distribution,
where only a few very rich people own a large amount.

\begin{itemize}
	\item The fraction of telephone numbers that receive calls per day is roughly equivalent to $1/k^2$
	\item The fraction of books bought is roughly proportional to $1/k^3$
	\item The fraction of scientific paper cited is roughly proportional to $1/k^3$
\end{itemize}

The degree distribution is not a Gaussian one,
but a \emph{Power Law distribution}.

	\subsubsection{Features} % (fold)
	\label{ssub:features}
		Let $f(k)$ be the fraction of items having the value $k$ then
		\begin{equation}
		\label{eq:powerlaw}
			f(k) = zk^{-\alpha}
		\end{equation}
		where $\alpha$ and $z$ are constants.\\
		Then $\log$ is applied to both sides so,
		\begin{equation}
			\log f(k) = \log z - \alpha\log k
		\end{equation}
		now one can easily see if the data follows a power law distribution in a coordinate system.
		If it follows this distribution,
		a straight line will form from the data.\\
		To estimate $\alpha$ one can simply fit line on the log-log axis.
		\begin{equation}
			\min_{\alpha}(\log(y) - \alpha\log(x))^2
		\end{equation}
	% subsubsection features (end)
% subsection power_law (end)

\subsection{Small World Phenomenon} % (fold)
\label{sub:small_world_phenomenon}
This Phenomenon the fact,
that most networks are quite densely connected
and that the distance is much lower than expected.
Milgram found out about this in his famous experiment in 1967,
where it took the letters an average of 6.2 hops to reach the target.
In todays network the number of hops 
and thereby the diameter are even lower.
On twitter it was at 4.67 and 4.74 on Facebook both in 2011.

The simple explanation is quite simple.
If one supposes that each person knows 100 people on a first name basis,
due to the exponential effects one can reach $100^5 = 10 Billion$ people in the 5\textsuperscript{th} step.
As the world only inhabits about 7 Billion people,
the chances of finding a connection is quite large.
% subsection small_world_phenomenon (end)

% section social_networks_structure_&_properties (end)